\section{Workbench integration}
There are other ways in which the workbench integration could be done. The java approach \ref{Use_Of_class_extention} and another Kotlin feature \ref{Use_of_scope_slots}. Both approaches would work and they both have their own advantages and disadvantages.

\subsection{Use of Scope Slots Function} \label{Use_of_scope_slots}
Kotlin supports scoped functions. These functions provide access to the Object and define scopes which can be accessed by the caller.

Instead of having a Workbench object which the user has to create and then use, the Workbench could be a scoped function with scopes for adding Explorers and Editors.

\begin{kotlincode}
createComposeWorkbench() {
    editors{
        editor{
            //define content of editor here
        }
    }
    explorers{
        explorer{
            //define content of explorer here
        }
    }
}
\end{kotlincode}

\subsection{Use of class extension} \label{Use_Of_class_extention}
In contrast to the used trailing lambda approach or the above mentioned scoped functions the workbench integration could be done with a more classical approach of extending and overriding a given class. 

\begin{kotlincode}
class MyWorkbenchEditor(): ComposeWorkbenchEditor {
    
    @Composable
    override fun content(){
        //The actual editor content
    }
}
\end{kotlincode}


\section{Internal Messaging System}
Instead of the embedded HiveMQ Broker and it's Clients, another internal concept could be used. Until now we didn't notice a lack of performance due to the messaging through the embedded Broker (Server). But it can be see as an over kill for a desktop application and may be become critical on larger applications with way more messages.

A internal Messaging System with out a network would be ways faster on transmission and initialization of it's infrastructure.

For example Kotlin's Channels could be an interesting approach to use as a messaging system. Channels offer by default concurrent access by Coroutines and filter for incoming messages. Implementations like BroadcastChannels indicate to use it as network like information exchange.